---
title: "INSPECT-SR Human Review"
subtitle: "Pinned guidance, evidence, and recorded reviewer decisions"
format:
  html:
    toc: true
    number-sections: true
  pdf:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
report_path <- Sys.getenv("INSPECT_SR_REPORT_JSON", unset = "")
if (!nzchar(report_path) || !file.exists(report_path)) {
  stop("INSPECT_SR_REPORT_JSON must point to an explicit, current review report model.")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  stop("The Quarto report requires the R package jsonlite; method packages are optional.")
}
report <- jsonlite::fromJSON(report_path, simplifyVector = FALSE)
checks <- report$checks
`%||%` <- function(x, y) if (is.null(x) || length(x) == 0) y else x
```

## Review overview

**`r report$report_status`**

| Field | Recorded value |
|---|---|
| Trial | `r report$trial_id` |
| Assessment | `r report$assessment_id` |
| Guidance | `r report$guidance_version` (`r report$guidance_sha256`) |
| Finalization | `r report$finalization_id %||% "None"` |

```{r}
if (is.null(report$judgments)) {
  cat("No human overall judgment is finalized for this report revision. No legacy score or computed trustworthiness category is displayed.")
} else {
  if (length(report$domain_judgments) > 0) {
    domain_table <- do.call(rbind, lapply(report$domain_judgments, function(x) {
      data.frame(domain_id = x$domain_id, judgment = x$judgment,
                 rationale = x$rationale, stringsAsFactors = FALSE)
    }))
    print(knitr::kable(domain_table, caption = "Human domain judgments"))
  }
  cat("**Overall human judgment:** ", report$judgments$overall$judgment, "\n\n", sep = "")
  cat("**Rationale:** ", report$judgments$overall$rationale, "\n\n", sep = "")
  if (!is.null(report$judgments$overall$justification)) {
    cat("**Lower overall judgment justification:** ", report$judgments$overall$justification, "\n\n", sep = "")
  }
  cat("**Finalization:** ", report$report_status, "\n", sep = "")
}
```

### Source versions

```{r}
if (length(report$source_versions) == 0) {
  cat("No source versions were attached to this report model.")
} else {
  source_table <- do.call(rbind, lapply(report$source_versions, function(x) {
    data.frame(source_id = x$source_id %||% NA_character_,
               source_version_id = x$source_version_id %||% NA_character_,
               sha256 = x$content_sha256 %||% NA_character_,
               stringsAsFactors = FALSE)
  }))
  knitr::kable(source_table)
}
```

```{r}
if (knitr::is_latex_output()) cat("\\newpage\n")
```

## Check records and evidence

Each check remains a distinct evidence and human-response record. Candidate method outputs are leads for review and never official responses.

```{r}
check_table <- do.call(rbind, lapply(checks, function(x) {
  data.frame(check_id = x$check_id,
             official_wording = x$official_wording,
             workflow_status = x$workflow_status,
             response = x$response %||% NA_character_,
             rationale = x$rationale %||% NA_character_,
             evidence_ids = paste(unlist(x$evidence_ids), collapse = "; "),
             stringsAsFactors = FALSE)
}))
knitr::kable(check_table, longtable = TRUE)
```

### Evidence locators, observations, and alternatives

```{r}
for (check in checks) {
  cat("\n\n#### Check ", check$check_id, "\n\n", check$official_wording, "\n\n", sep = "")
  records <- c(check$evidence_records, check$manual_evidence, check$candidate_evidence)
  if (length(records) == 0) {
    cat("No evidence records are attached.\n\n")
  } else {
    rows <- do.call(rbind, lapply(records, function(item) {
      data.frame(kind = item$record_type %||% item$candidate_kind %||% "candidate",
                 evidence_or_candidate_id = item$evidence_id %||% item$candidate_id %||% NA_character_,
                 locator = item$locator %||% item$source_locator %||% NA_character_,
                 observation_or_details = item$observation %||% item$details %||% "",
                 explanation_or_limitations = item$explanation %||% item$limitations %||% "",
                 alternate_explanations = paste(unlist(item$alternate_explanations), collapse = "; "),
                 stringsAsFactors = FALSE)
    }))
    print(knitr::kable(rows))
  }
}
```

## Method coverage and reviewer history

```{r}
if (length(report$method_receipts) == 0) {
  cat("No method receipts were attached. Missing receipts are not negative findings.")
} else {
  method_table <- do.call(rbind, lapply(report$method_receipts, function(x) {
    data.frame(method_id = x$method_id %||% NA_character_,
               execution = x$execution %||% NA_character_,
               n_eligible = x$n_eligible %||% NA_integer_,
               n_evaluated = x$n_evaluated %||% NA_integer_,
               n_failed = x$n_failed %||% NA_integer_,
               stringsAsFactors = FALSE)
  }))
  knitr::kable(method_table)
}
```

```{r}
if (length(report$reviewer_submissions) == 0) {
  cat("No reviewer submissions were attached.")
} else {
  review_history <- do.call(rbind, lapply(report$reviewer_submissions, function(x) {
    data.frame(reviewer_id = x$reviewer_id %||% NA_character_,
               submission_id = x$submission_id %||% NA_character_,
               source_snapshot_sha256 = x$source_snapshot_sha256 %||% NA_character_,
               workflow_status = x$workflow_status %||% NA_character_,
               stringsAsFactors = FALSE)
  }))
  knitr::kable(review_history)
}
if (!is.null(report$adjudication)) {
  cat("\n\n**Adjudication ID:** ", report$adjudication$adjudication_id, "\n", sep = "")
}
```

## Unresolved items

```{r}
if (length(report$unresolved_items) == 0) {
  cat("No checks remain pending or unassessed in this review record.")
} else {
  unresolved <- do.call(rbind, lapply(report$unresolved_items, function(x) {
    data.frame(check_id = x$check_id,
               workflow_status = x$workflow_status,
               response = x$response %||% NA_character_,
               stringsAsFactors = FALSE)
  }))
  knitr::kable(unresolved)
}
```
