---
title: "Visual Forensics Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes text-driven visual-forensics heuristics from figure-caption extraction.
It also reports pilot human-in-the-loop plot digitization coverage.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "visual", study_id)

required <- c("visual_row_results.csv", "visual_summary.csv", "visual_digitized_values.csv")
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

row_results <- read.csv(file.path(report_dir, "visual_row_results.csv"), check.names = FALSE)
summary_tbl <- read.csv(file.path(report_dir, "visual_summary.csv"), check.names = FALSE)
digitized <- read.csv(file.path(report_dir, "visual_digitized_values.csv"), check.names = FALSE)

compact_character <- function(x, width = 44) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  too_long <- nchar(x) > width
  x[too_long] <- paste0(substr(x[too_long], 1, width - 3), "...")
  x
}

compact_df <- function(df, cols = NULL, n = 25, char_width = 44) {
  out <- df
  if (!is.null(cols)) {
    keep <- intersect(cols, names(out))
    out <- out[, keep, drop = FALSE]
  }
  if (nrow(out) > n) {
    out <- utils::head(out, n)
  }
  is_char_like <- vapply(out, function(col) is.character(col) || is.factor(col), logical(1))
  out[is_char_like] <- lapply(out[is_char_like], compact_character, width = char_width)
  out
}
```

## Interpretation Key

- `n_figure_mentions`: number of caption-like figure mentions extracted from PDF text.
- `n_duplicate_pairs`: number of near-duplicate caption pairs above similarity threshold.
- `near_duplicate_rate`: duplicate-pair burden relative to extracted figure mentions.
- `n_numbering_gaps`: count of missing figure numbers between observed min and max.
- `numbering_gap_flag`: quick signal that sequence gaps exist in extracted numbering.
- `n_digitized_figures`: unique figures with digitized point data.
- `n_digitized_series`: unique digitized series across included figures.
- `n_digitized_points`: total extracted points available for downstream analyses.
- `digitization_ready`: whether non-empty digitized data are available in this run.

Digitization values come from manual `metaDigitise` calibration/click workflows and should be treated as measurement data with operator uncertainty.

```{r}
knitr::kable(summary_tbl, digits = 4)
```

## Plot Digitization Coverage

```{r}
knitr::kable(summary_tbl[, c(
  "trial_id",
  "n_digitized_figures",
  "n_digitized_series",
  "n_digitized_points",
  "digitization_ready"
)], digits = 4)
```

```{r}
if (nrow(digitized) > 0) {
  knitr::kable(
    compact_df(
      digitized,
      cols = c(
        "study_id", "figure_id", "panel_id", "series_id",
        "x_value", "y_value", "x_unit", "y_unit",
        "extract_confidence", "source_image"
      ),
      n = 25,
      char_width = 38
    ),
    digits = 4
  )
} else {
  cat("No digitized plot values available yet (pilot capture not completed).")
}
```

## Row-Level Checks

```{r}
knitr::kable(
  compact_df(
    row_results,
    cols = c(
      "trial_id",
      "n_figure_mentions",
      "n_duplicate_pairs",
      "n_numbering_gaps",
      "numbering_gaps",
      "n_digitized_figures",
      "n_digitized_series",
      "n_digitized_points",
      "digitization_ready"
    ),
    n = 20,
    char_width = 36
  )
)
```
