---
title: "LungTIME-C01 Randomization Forensics Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes randomization-forensics signals from baseline characteristics in:

- `s41591-025-04181-w.pdf`
- `41591_2025_4181_MOESM1_ESM.pdf`

Inputs are generated by:

- `scripts/extract_randomization_table1.py`
- `scripts/build_randomization_inputs.py`
- `scripts/run_randomization_forensics.R`

## Load Inputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
input_dir <- file.path(repo_root, "reports", "randomization", "lungtime")

required_files <- c(
  "row_level_results.csv",
  "pooled_pvalues.csv",
  "simdistr_variable_pvalues.csv",
  "simdistr_combined_pvalues.csv"
)
missing_files <- required_files[!file.exists(file.path(input_dir, required_files))]
if (length(missing_files) > 0) {
  stop(
    "Missing expected analysis outputs: ",
    paste(missing_files, collapse = ", "),
    ". Run scripts/run_randomization_forensics.R first."
  )
}

row_level <- read.csv(file.path(input_dir, "row_level_results.csv"), check.names = FALSE)
pooled <- read.csv(file.path(input_dir, "pooled_pvalues.csv"), check.names = FALSE)
sim_var <- read.csv(file.path(input_dir, "simdistr_variable_pvalues.csv"), check.names = FALSE)
sim_combined <- read.csv(file.path(input_dir, "simdistr_combined_pvalues.csv"), check.names = FALSE)

ascii_text <- function(x) {
  x <- gsub("≥", ">=", x, fixed = TRUE)
  x <- gsub("–", "-", x, fixed = TRUE)
  x
}

row_level$variable <- ascii_text(row_level$variable)
row_level$level <- ascii_text(row_level$level)
sim_var$variable <- ascii_text(sim_var$variable)
sim_var$level <- ascii_text(sim_var$level)
```

## Trial Metadata Snapshot

```{r}
meta_path <- file.path(repo_root, "data", "processed", "randomization", "lungtime", "randomization_metadata.csv")
if (file.exists(meta_path)) {
  metadata <- read.csv(meta_path, check.names = FALSE)
  knitr::kable(metadata)
} else {
  cat("Metadata file not found at:", meta_path)
}
```

## Pooled Summary Metrics

### Interpretation Key (Heathers-aligned)

The metrics below are randomization-forensics checks on baseline Table 1 distributions, aligned with the screening logic discussed in Heathers' overview of STALT/CSF-style methods:

- `n_rows_reported`: number of baseline rows with manuscript-reported p-values.
- `n_rows_recalc`: number of baseline rows with recalculated row-level p-values.
- `stouffer_reported`: one-sided Stouffer combination of reported row p-values.
- `stouffer_recalc`: one-sided Stouffer combination of recalculated row p-values.
- `fisher_reported`: Fisher combination of reported row p-values.
- `fisher_recalc`: Fisher combination of recalculated row p-values.
- `simdistr_combined_pvalue`: simulation-based combined p-value from `simdistr`.

Interpretation rule of thumb:

- Smaller combined p-values indicate less compatibility with expected random baseline balance.
- Larger combined p-values indicate no low-tail signal for imbalance under these checks.
- No single metric is dispositive; methods are screening tools and should be interpreted with design/context checks from protocol and data provenance.

```{r}
knitr::kable(pooled, digits = 6)
knitr::kable(sim_combined, digits = 6)
```

```{r}
n_rows <- nrow(row_level)
n_flagged_delta <- sum(row_level$flagged_p_delta_0_05, na.rm = TRUE)
cat("Rows analyzed:", n_rows, "\n")
cat("Rows with |reported p - recalculated p| >= 0.05:", n_flagged_delta, "\n")
```

## Row-Level Signals

### Lowest recalculated p-values

```{r}
row_by_p <- row_level[order(row_level$row_chisq_p, na.last = TRUE), ]
knitr::kable(head(row_by_p[, c("variable", "level", "row_chisq_p", "reported_p")], 10), digits = 5)
```

### Largest reported vs recalculated p-value gaps

```{r}
row_by_delta <- row_level[order(-row_level$abs_p_delta, na.last = TRUE), ]
knitr::kable(
  head(row_by_delta[, c("variable", "level", "reported_p", "row_chisq_p", "abs_p_delta")], 10),
  digits = 5
)
```

## `simdistr` Variable-Level Signals

```{r}
sim_by_p <- sim_var[order(sim_var$simdistr_pvalue, na.last = TRUE), ]
knitr::kable(head(sim_by_p[, c("variable", "level", "simdistr_pvalue")], 15), digits = 5)
```

## Diagnostics

### Distribution of recalculated row p-values

```{r}
hist(
  row_level$row_chisq_p,
  breaks = 10,
  col = "gray80",
  border = "white",
  main = "Row-level Recalculated P-values",
  xlab = "row_chisq_p"
)
abline(v = 0.05, col = "red", lwd = 2, lty = 2)
```

### Reported vs recalculated row p-values

```{r}
plot(
  row_level$reported_p,
  row_level$row_chisq_p,
  pch = 19,
  col = "steelblue",
  xlab = "Reported p-value",
  ylab = "Recalculated row p-value",
  main = "Reported vs Recalculated Baseline P-values"
)
abline(0, 1, col = "darkgray", lwd = 2)
abline(h = 0.05, col = "red", lty = 2)
abline(v = 0.05, col = "red", lty = 2)
```

### Lowest `simdistr` variable-level p-values

```{r}
plot_df <- head(sim_by_p, 10)
barplot(
  height = rev(plot_df$simdistr_pvalue),
  names.arg = rev(paste(plot_df$variable, plot_df$level, sep = " / ")),
  horiz = TRUE,
  las = 1,
  col = "gray75",
  border = NA,
  main = "Lowest simdistr Variable-level P-values",
  xlab = "simdistr p-value",
  xlim = c(0, 1)
)
abline(v = 0.05, col = "red", lty = 2)
```

## Interpretation Notes

- This is a baseline-balance forensic screen, not a causal efficacy analysis.
- Row-level p-values depend on one-vs-rest encodings for multi-level variables.
- Reported manuscript p-values may use test choices that differ from recalculation methods.
- Joint p-value methods are sensitive to correlation among baseline variables.
