---
title: "Registration Congruence Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report compares manuscript and protocol claims for trial registration and methods congruence.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "registration", study_id)

required <- c("registration_row_results.csv", "registration_summary.csv")
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

row_results <- read.csv(file.path(report_dir, "registration_row_results.csv"), check.names = FALSE)
summary_tbl <- read.csv(file.path(report_dir, "registration_summary.csv"), check.names = FALSE)

compact_character <- function(x, width = 44) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  too_long <- nchar(x) > width
  x[too_long] <- paste0(substr(x[too_long], 1, width - 3), "...")
  x
}

compact_df <- function(df, cols = NULL, n = 20, char_width = 44) {
  out <- df
  if (!is.null(cols)) {
    keep <- intersect(cols, names(out))
    out <- out[, keep, drop = FALSE]
  }
  if (nrow(out) > n) {
    out <- utils::head(out, n)
  }
  is_char_like <- vapply(out, function(col) is.character(col) || is.factor(col), logical(1))
  out[is_char_like] <- lapply(out[is_char_like], compact_character, width = char_width)
  out
}
```

## Interpretation Key

- `n_claims`: number of report-versus-protocol claims checked.
- `n_mismatch`: number of claims where extracted values do not match.
- `mismatch_rate`: mismatch burden across claims.
- `n_missing`: claims with missing extracted value from report or protocol.
- `missing_rate`: missingness burden that can reduce confidence in congruence checks.

```{r}
knitr::kable(summary_tbl, digits = 4)
```

## Claim-Level Table

```{r}
knitr::kable(
  compact_df(
    row_results,
    cols = c(
      "claim",
      "report_value",
      "protocol_value",
      "match_status",
      "evidence_page_report",
      "evidence_page_protocol",
      "extract_confidence"
    ),
    n = 25,
    char_width = 40
  )
)
```
