---
title: "Registration Congruence Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report compares source-linked manuscript and protocol claims with ClinicalTrials.gov metadata when an NCT identifier is available. Automated matches and mismatches are evidence comparisons, not INSPECT judgments. Registration timing, results-posting, and publication-linkage fields are qualified metadata screens; none establishes a concern or protocol violation.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "registration", study_id)
data_dir <- file.path(repo_root, "data", "processed", "registration", study_id)

required <- c("registration_row_results.csv", "registration_summary.csv")
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

row_results <- read.csv(file.path(report_dir, "registration_row_results.csv"), check.names = FALSE)
summary_tbl <- read.csv(file.path(report_dir, "registration_summary.csv"), check.names = FALSE)
history_path <- file.path(report_dir, "registration_history_events.csv")
history_events <- if (file.exists(history_path)) {
  read.csv(history_path, check.names = FALSE)
} else {
  data.frame()
}
history_status_path <- file.path(report_dir, "registration_history_status_v1.csv")
history_status <- if (file.exists(history_status_path)) {
  read.csv(history_status_path, check.names = FALSE)
} else {
  data.frame(history_status = "not_provided", history_completeness = "unknown")
}
fetch_metadata_path <- file.path(data_dir, "metadata", "registration_registry_fetch_metadata.csv")
fetch_metadata <- if (file.exists(fetch_metadata_path)) {
  read.csv(fetch_metadata_path, check.names = FALSE)
} else {
  data.frame()
}
current_registry_path <- file.path(data_dir, "inputs", "registration_registry_current.csv")
current_registry <- if (file.exists(current_registry_path)) {
  read.csv(current_registry_path, check.names = FALSE)
} else {
  data.frame()
}

compact_character <- function(x, width = 44) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  too_long <- nchar(x) > width
  x[too_long] <- paste0(substr(x[too_long], 1, width - 3), "...")
  x
}

compact_df <- function(df, cols = NULL, n = 20, char_width = 44) {
  out <- df
  if (!is.null(cols)) {
    keep <- intersect(cols, names(out))
    out <- out[, keep, drop = FALSE]
  }
  if (nrow(out) > n) {
    out <- utils::head(out, n)
  }
  is_char_like <- vapply(out, function(col) is.character(col) || is.factor(col), logical(1))
  out[is_char_like] <- lapply(out[is_char_like], compact_character, width = char_width)
  out
}
```

## Interpretation Key

- `n_claims`: total claim rows evaluated, including report-protocol and registry-derived rows.
- `n_claims_assessed`: rows with enough information to classify as `match` or `mismatch`.
- `n_mismatch`: assessed rows classified as mismatch.
- `mismatch_rate`: `n_mismatch / n_claims_assessed`; indeterminate and not-assessed rows are excluded.
- `n_missing`: rows with missing report or protocol values.
- `missing_rate`: missing report/protocol burden across all claim rows.
- `prospective_registration_status`: a metadata screen comparing first submission with registered start. First-posted and actual recruitment-start dates are retained separately.
- `n_major_registry_history_changes`: local history-event rows marked medium/high severity.
- `results_overdue_screen_status`: a 365-day metadata screen after primary completion; not an assessment result.
- `publication_linkage_screen_status`: whether supplied publication identifiers were detected in registry references; non-detection is not evidence that no linked publication exists.
- `registry_history_status`, `registry_history_completeness`, and `registry_history_chronology_status`: describe usable supplied history, with completeness left unknown unless established by its source.

Classification labels:

- `match`: available extracted values agree under the implemented screen.
- `mismatch`: available extracted source claims conflict under the implemented comparison.
- `indeterminate`: the source contains insufficient or ambiguous information for automated classification.
- `not_assessed`: the screen is not applicable or no eligible registry/source data were available.

```{r}
knitr::kable(summary_tbl, digits = 4)
```

## Registry History Availability

History availability and chronology are separate from detected change events. No detected changes do not establish that the supplied history is complete.

```{r}
knitr::kable(history_status)
```

## Registry Source

```{r}
if (nrow(fetch_metadata) == 0) {
  cat("No registry fetch metadata was available.\n")
} else {
  knitr::kable(
    compact_df(
      fetch_metadata,
      cols = c(
        "registry_id",
        "registry_id_source",
        "registry_current_source",
        "allow_network",
        "fetch_status",
        "fetch_message",
        "api_url",
        "source_version",
        "source_sha256"
      ),
      n = 5,
      char_width = 42
    )
  )
}
```

```{r}
if (nrow(current_registry) > 0) {
  knitr::kable(
    compact_df(
      current_registry,
      cols = c(
        "registry_id",
        "study_type",
        "overall_status",
        "start_date",
        "registered_start_date",
        "start_date_type",
        "actual_recruitment_start_date",
        "first_submitted_date",
        "study_first_posted_date",
        "primary_completion_date",
        "has_results",
        "enrollment_count",
        "allocation",
        "masking"
      ),
      n = 5,
      char_width = 36
    )
  )
} else {
  cat("No normalized ClinicalTrials.gov current record was available.\n")
}
```

## Report-Protocol Claims

```{r}
report_protocol <- row_results[row_results$claim_category == "report_protocol", , drop = FALSE]
knitr::kable(
  compact_df(
    report_protocol,
    cols = c(
      "claim_id",
      "report_value",
      "protocol_value",
      "assessment_status",
      "page_ref",
      "report_evidence",
      "protocol_evidence",
      "report_negated",
      "protocol_negated",
      "population",
      "role",
      "severity"
    ),
    n = 25,
    char_width = 38
  )
)
```

## ClinicalTrials.gov Current-Record Claims

```{r}
registry_claims <- row_results[row_results$claim_category != "report_protocol", , drop = FALSE]
if (nrow(registry_claims) == 0) {
  cat("No ClinicalTrials.gov-derived claim rows were available.\n")
} else {
  knitr::kable(
    compact_df(
      registry_claims,
      cols = c(
        "claim_id",
        "assessment_status",
        "screen_status",
        "severity",
        "report_value",
        "registry_value",
        "notes"
      ),
      n = 30,
      char_width = 34
    )
  )
}
```

## Registry History Events

This table contains only dated changes detected in supplied local history. Its absence or emptiness does not establish that history was absent or complete; see the availability and chronology record above.

```{r}
if (nrow(history_events) == 0) {
  cat("No local registry-history events were available.\n")
} else {
  knitr::kable(
    compact_df(
      history_events,
      cols = c(
        "event_date",
        "registry_field",
        "old_value",
        "new_value",
        "severity",
        "notes"
      ),
      n = 30,
      char_width = 34
    )
  )
}
```
