---
title: "Meta-Forensics Aggregation Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes category coverage and source-linked screening signals. It does not calculate a study-level score, assign a risk tier, or produce an INSPECT judgment. Screening signals remain candidates for independent human review.

## Load Outputs

```{r}
reports_root <- Sys.getenv("FORENSICS_REPORTS_ROOT", unset = "")
if (!nzchar(reports_root)) stop("FORENSICS_REPORTS_ROOT must point to this run's reports directory.")
report_dir <- file.path(reports_root, "meta")

required <- c(
  "meta_evidence_coverage_v2_out.csv",
  "meta_candidate_concerns_v1_out.csv",
  "meta_coverage_summary_v1.csv"
)
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

coverage <- read.csv(file.path(report_dir, "meta_evidence_coverage_v2_out.csv"), check.names = FALSE)
candidate_concerns <- read.csv(file.path(report_dir, "meta_candidate_concerns_v1_out.csv"), check.names = FALSE)
coverage_summary <- read.csv(file.path(report_dir, "meta_coverage_summary_v1.csv"), check.names = FALSE)
```

## Coverage

Coverage counts are not additive judgments. `failed` and `unsupported` remain missing when category sources do not distinguish those states. A category with only missing metrics is unavailable for assessment; it is not evidence of a reassuring result.

```{r}
knitr::kable(coverage_summary, digits = 4)
```

## Category Evidence and Coverage

```{r}
knitr::kable(coverage, digits = 4)
```

## Source-Linked Candidate Concerns

```{r}
if (nrow(candidate_concerns) > 0) {
  knitr::kable(candidate_concerns, digits = 4)
} else {
  cat("No source-linked screening signals were supplied to this summary.")
}
```
