---
title: "Randomization Forensics Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes randomization-forensics signals from baseline characteristics for the configured study.

Inputs are generated by:

- `scripts/extract_randomization_table1.py`
- `scripts/build_randomization_inputs.py`
- `scripts/run_randomization_forensics.R`

## Load Inputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
study_label <- Sys.getenv("FORENSICS_STUDY_TITLE", study_id)
reports_root <- Sys.getenv("FORENSICS_REPORTS_ROOT", unset = "")
processed_root <- Sys.getenv("FORENSICS_PROCESSED_ROOT", unset = "")
if (!nzchar(reports_root) || !nzchar(processed_root)) {
  stop("FORENSICS_REPORTS_ROOT and FORENSICS_PROCESSED_ROOT must point to this run.")
}
input_dir <- file.path(reports_root, "randomization")

required_files <- c(
  "row_level_results_v2.csv",
  "pooled_descriptive_v2.csv",
  "reported_test_records_v1.csv",
  "allocation_arithmetic_v1.csv",
  "randomization_run_receipt_v1.csv",
  "simdistr_variable_pvalues_v1.csv",
  "simdistr_combined_descriptive_v1.csv"
)
missing_files <- required_files[!file.exists(file.path(input_dir, required_files))]
if (length(missing_files) > 0) {
  stop(
    "Missing expected analysis outputs: ",
    paste(missing_files, collapse = ", "),
    ". Run scripts/run_randomization_forensics.R first."
  )
}

row_level <- read.csv(file.path(input_dir, "row_level_results_v2.csv"), check.names = FALSE)
pooled <- read.csv(file.path(input_dir, "pooled_descriptive_v2.csv"), check.names = FALSE)
reported_tests <- read.csv(file.path(input_dir, "reported_test_records_v1.csv"), check.names = FALSE)
allocation <- read.csv(file.path(input_dir, "allocation_arithmetic_v1.csv"), check.names = FALSE)
run_receipt <- read.csv(file.path(input_dir, "randomization_run_receipt_v1.csv"), check.names = FALSE)
sim_var <- read.csv(file.path(input_dir, "simdistr_variable_pvalues_v1.csv"), check.names = FALSE)
sim_combined <- read.csv(file.path(input_dir, "simdistr_combined_descriptive_v1.csv"), check.names = FALSE)

ascii_text <- function(x) {
  x <- gsub("≥", ">=", x, fixed = TRUE)
  x <- gsub("–", "-", x, fixed = TRUE)
  x
}

row_level$variable <- ascii_text(row_level$variable)
row_level$level <- ascii_text(row_level$level)
if ("variable" %in% names(sim_var)) sim_var$variable <- ascii_text(sim_var$variable)
if ("level" %in% names(sim_var)) sim_var$level <- ascii_text(sim_var$level)
```

## Trial Metadata Snapshot

```{r}
meta_path <- if (nzchar(processed_root)) {
  file.path(processed_root, "randomization", "randomization_metadata.csv")
} else {
  ""
}
if (file.exists(meta_path)) {
  metadata <- read.csv(meta_path, check.names = FALSE)
  knitr::kable(metadata)
} else {
  cat("Metadata file not found at:", meta_path)
}
```

## Run and Allocation Receipts

These records describe run settings and, when explicitly supplied, a narrow allocation-count compatibility check. The allocation arithmetic is separate from baseline hypothesis tests and is not a trial trustworthiness judgment.

```{r}
knitr::kable(run_receipt)
knitr::kable(allocation)
knitr::kable(pooled)
```

## Reported Variable Tests

Reported tests are preserved once per source test record. Scope, method, tail, and analysis population remain unknown unless the source explicitly supplies them. Inequality symbols remain separate from the numeric value.

```{r}
knitr::kable(reported_tests)
```

```{r}
n_rows <- nrow(row_level)
cat("One-versus-rest recalculated rows:", n_rows, "\n")
cat("Reported-versus-recalculated comparisons made:", sum(row_level$comparison_status == "comparable"), "\n")
```

## Row-Level Signals

### Lowest recalculated p-values

```{r}
row_by_p <- row_level[order(row_level$row_chisq_p, na.last = TRUE), ]
knitr::kable(head(row_by_p[, c("parent_variable", "level", "row_chisq_p", "comparison_status")], 10), digits = 5)
```

### Comparison status

```{r}
comparison_counts <- as.data.frame(table(row_level$comparison_status, useNA = "ifany"))
names(comparison_counts) <- c("comparison_status", "n_rows")
knitr::kable(comparison_counts)
cat("Reported and recalculated tests are not compared when their scope, method, tail, or population is unknown.")
```

## `simdistr` Variable-Level Signals

```{r}
if ("simdistr_pvalue" %in% names(sim_var)) {
  sim_by_p <- sim_var[order(sim_var$simdistr_pvalue, na.last = TRUE), ]
  knitr::kable(head(sim_by_p[, c("variable", "level", "simdistr_pvalue", "execution_status")], 15), digits = 5)
} else {
  knitr::kable(sim_var)
  knitr::kable(sim_combined)
}
```

## Diagnostics

### Distribution of recalculated row p-values

```{r}
recalculated_p <- suppressWarnings(as.numeric(row_level$row_chisq_p))
if (any(is.finite(recalculated_p))) {
  hist(
    recalculated_p[is.finite(recalculated_p)],
    breaks = 10,
    col = "gray80",
    border = "white",
    main = "Row-level Recalculated P-values (Expert Opt-In)",
    xlab = "row_chisq_p"
  )
  abline(v = 0.05, col = "red", lwd = 2, lty = 2)
} else {
  cat("No inferential row-level P values were requested or supported for the recorded design.")
}
```

### Lowest `simdistr` variable-level p-values

```{r}
if ("simdistr_pvalue" %in% names(sim_var)) {
  plot_df <- head(sim_by_p, 10)
  barplot(
    height = rev(plot_df$simdistr_pvalue),
    names.arg = rev(paste(plot_df$variable, plot_df$level, sep = " / ")),
    horiz = TRUE,
    las = 1,
    col = "gray75",
    border = NA,
    main = "simdistr Variable-Level Outputs (Expert Opt-In)",
    xlab = "simdistr p-value",
    xlim = c(0, 1)
  )
} else {
  cat("No simdistr values were produced:", sim_var$reason[[1]])
}
```

## Interpretation Notes

- This is a baseline-balance forensic screen, not a causal efficacy analysis.
- Recalculated categorical rows use one-versus-rest Pearson 2x2 tests; levels within a parent variable are correlated.
- Reported test method, scope, tail, and analysis population are not inferred from the displayed P value.
- Row-level differences are not labeled computational contradictions when the reported test definition is unknown.
- Combined `simdistr` outputs are marked uncalibrated when dependence among variables is unknown.
