---
title: "Transparency Evidence Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes offline transparency evidence extracted from source documents. It is an evidence map for human review, not an automated quality score. No network calls, LLM calls, or direct `metacheck` package dependency are used in this v1 category.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "transparency", study_id)

required <- c(
  "transparency_summary.csv",
  "transparency_open_practices.csv",
  "transparency_repository_links.csv",
  "transparency_preregistration_links.csv",
  "research_object_sources.csv"
)
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

summary_tbl <- read.csv(file.path(report_dir, "transparency_summary.csv"), check.names = FALSE)
open_practices <- read.csv(file.path(report_dir, "transparency_open_practices.csv"), check.names = FALSE)
repositories <- read.csv(file.path(report_dir, "transparency_repository_links.csv"), check.names = FALSE)
prereg <- read.csv(file.path(report_dir, "transparency_preregistration_links.csv"), check.names = FALSE)
sources <- read.csv(file.path(report_dir, "research_object_sources.csv"), check.names = FALSE)
```

## Summary

`transparency_evidence_burden` is a triage-oriented missing-evidence indicator based on detected open-practice statements and on-request language. It should not be interpreted as a validity, misconduct, or quality ranking.

```{r}
knitr::kable(summary_tbl, digits = 4)
```

## Source Provenance

```{r}
knitr::kable(sources)
```

## Open-Practice Evidence

```{r}
if (nrow(open_practices) == 0) {
  cat("No open-practice evidence statements were detected by the offline text scan.")
} else {
  display <- open_practices[, intersect(
    c("practice", "is_open", "category", "location", "source_pdf", "page", "evidence_text"),
    names(open_practices)
  ), drop = FALSE]
  knitr::kable(display)
}
```

## Repository Links

```{r}
if (nrow(repositories) == 0) {
  cat("No supported repository links were detected.")
} else {
  knitr::kable(repositories[, intersect(
    c("repository_type", "url", "source_pdf", "page", "context"),
    names(repositories)
  ), drop = FALSE])
}
```

## Preregistration And Registry Links

```{r}
if (nrow(prereg) == 0) {
  cat("No preregistration or registry links/identifiers were detected.")
} else {
  knitr::kable(prereg[, intersect(
    c("link_type", "url_or_id", "source_pdf", "page", "context"),
    names(prereg)
  ), drop = FALSE])
}
```
