---
title: "Numeric Integrity Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report summarizes numeric-integrity checks aligned with Heathers' data-technique family:

- internal rounding consistency for count-percent table cells
- `scrutiny` GRIM / GRIMMER / DEBIT and duplicate-value checks
- rounding-bias diagnostics for reported decimal patterns
- statistical-consistency checks via `statcheck`

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "numeric", study_id)

required <- c(
  "numeric_row_results.csv",
  "numeric_summary.csv",
  "numeric_package_status.csv",
  "numeric_scrutiny_grim_raw.csv",
  "numeric_scrutiny_grim_audit.csv",
  "numeric_scrutiny_grimmer_raw.csv",
  "numeric_scrutiny_grimmer_audit.csv",
  "numeric_scrutiny_debit_raw.csv",
  "numeric_scrutiny_debit_audit.csv",
  "numeric_scrutiny_duplicates.csv",
  "numeric_scrutiny_rounding_bias.csv",
  "numeric_statcheck_raw.csv",
  "numeric_standardized_results.csv"
)
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

row_results <- read.csv(file.path(report_dir, "numeric_row_results.csv"), check.names = FALSE)
summary_tbl <- read.csv(file.path(report_dir, "numeric_summary.csv"), check.names = FALSE)
pkg_status <- read.csv(file.path(report_dir, "numeric_package_status.csv"), check.names = FALSE)
grim_raw <- read.csv(file.path(report_dir, "numeric_scrutiny_grim_raw.csv"), check.names = FALSE)
grim_audit <- read.csv(file.path(report_dir, "numeric_scrutiny_grim_audit.csv"), check.names = FALSE)
grimmer_raw <- read.csv(file.path(report_dir, "numeric_scrutiny_grimmer_raw.csv"), check.names = FALSE)
grimmer_audit <- read.csv(file.path(report_dir, "numeric_scrutiny_grimmer_audit.csv"), check.names = FALSE)
debit_raw <- read.csv(file.path(report_dir, "numeric_scrutiny_debit_raw.csv"), check.names = FALSE)
debit_audit <- read.csv(file.path(report_dir, "numeric_scrutiny_debit_audit.csv"), check.names = FALSE)
duplicates_raw <- read.csv(file.path(report_dir, "numeric_scrutiny_duplicates.csv"), check.names = FALSE)
rounding_bias <- read.csv(file.path(report_dir, "numeric_scrutiny_rounding_bias.csv"), check.names = FALSE)
statcheck_raw <- read.csv(file.path(report_dir, "numeric_statcheck_raw.csv"), check.names = FALSE)
standardized <- read.csv(file.path(report_dir, "numeric_standardized_results.csv"), check.names = FALSE)

compact_character <- function(x, width = 48) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  too_long <- nchar(x) > width
  x[too_long] <- paste0(substr(x[too_long], 1, width - 3), "...")
  x
}

compact_df <- function(df, cols = NULL, n = 20, char_width = 48) {
  out <- df
  if (!is.null(cols)) {
    keep <- intersect(cols, names(out))
    out <- out[, keep, drop = FALSE]
  }
  if (nrow(out) > n) {
    out <- utils::head(out, n)
  }
  is_char_like <- vapply(out, function(col) is.character(col) || is.factor(col), logical(1))
  out[is_char_like] <- lapply(out[is_char_like], compact_character, width = char_width)
  out
}

render_table <- function(df, note, cols = NULL, n = 20, digits = 4, char_width = 48) {
  if (nrow(df) > 0) {
    knitr::kable(compact_df(df, cols = cols, n = n, char_width = char_width), digits = digits)
  } else {
    cat(note)
  }
}
```

## Section 4 Summary Metrics Key

These are screening indicators from Heathers' data-techniques framework, not proof of misconduct.

- `n_rows`: number of categorical count-percent cells checked for arithmetic consistency.
- `n_rounding_flags`: rows with `|reported_percent - computed_percent| >= 0.2`.
- `rounding_flag_rate`: `n_rounding_flags / n_rows`; larger values suggest widespread reporting drift.
- `median_abs_percent_delta`, `max_abs_percent_delta`: typical and worst discrepancy magnitude.
- `scrutiny_cases_n`: total canonical rows prepared for scrutiny-family methods.
- `grim_cases`, `grim_incons_cases`: testable rows and inconsistency count from `scrutiny::grim_map`.
- `grimmer_cases`, `grimmer_incons_cases`: testable rows and inconsistency count from `scrutiny::grimmer_map`.
- `debit_cases`, `debit_incons_cases`: binary-proportion rows testable by DEBIT and their inconsistency count.
- `duplicate_flag_rows`: rows with at least one duplicated field (`x`, `sd`, or `n`) in duplicate checks.
- `rounding_bias_groups`: `(trial_id, digits_x)` groups assessed for directional rounding imbalance.
- `statcheck_cases`, `statcheck_errors`, `statcheck_decision_errors`: parsed test rows, any inconsistencies, and significance-changing inconsistencies.
- `scrutiny_seq_enabled`: whether optional sequence-space checks were executed.

Empty method tables can mean "no eligible rows", "package unavailable", or execution failure; inspect `numeric_package_status.csv` execution notes for attribution.

```{r}
if (nrow(summary_tbl) > 0) {
  summary_long <- data.frame(
    metric = names(summary_tbl),
    value = as.character(summary_tbl[1, ]),
    stringsAsFactors = FALSE
  )
  knitr::kable(summary_long)
} else {
  cat("No summary rows available.")
}
```

## Package Availability

```{r}
render_table(
  pkg_status,
  "No package-status output.",
  cols = c("package", "installed", "version", "objective", "executed", "execution_note"),
  n = 20,
  char_width = 42
)
```

## GRIM Results

```{r}
render_table(
  grim_audit,
  "No GRIM audit output (package unavailable or no GRIM-eligible rows).",
  n = 20
)
```

```{r}
render_table(
  grim_raw,
  "No GRIM row-level output.",
  cols = c("case_id", "source_unit", "x", "n", "consistency", "probability"),
  n = 20
)
```

## GRIMMER Results

```{r}
render_table(
  grimmer_audit,
  "No GRIMMER audit output (package unavailable or no GRIMMER-eligible rows).",
  n = 20
)
```

```{r}
render_table(
  grimmer_raw,
  "No GRIMMER row-level output.",
  cols = c("case_id", "variable", "level", "group", "x", "sd", "n", "consistency", "reason"),
  n = 20,
  char_width = 36
)
```

## DEBIT Results

```{r}
render_table(
  debit_audit,
  "No DEBIT audit output (package unavailable or no DEBIT-eligible rows).",
  n = 20
)
```

```{r}
render_table(
  debit_raw,
  "No DEBIT row-level output.",
  cols = c("case_id", "source_unit", "x", "sd", "n", "consistency", "rounding"),
  n = 20,
  char_width = 40
)
```

## Duplication And Rounding-Bias Results

```{r}
render_table(
  duplicates_raw,
  "No duplicate-check rows available.",
  cols = c("case_id", "variable", "level", "group", "x_dup", "sd_dup", "n_dup", "x_n", "sd_n", "n_n"),
  n = 20,
  char_width = 36
)
```

```{r}
render_table(
  rounding_bias,
  "No rounding-bias groups available.",
  cols = c("trial_id", "digits_x", "n_values", "bias_up", "bias_down", "abs_bias_gap", "anomaly_flag"),
  n = 20
)
```

## Statcheck Results

```{r}
if (nrow(statcheck_raw) > 0) {
  statcheck_ranked <- statcheck_raw[order(statcheck_raw$error, decreasing = TRUE), ]
  knitr::kable(
    compact_df(
      statcheck_ranked,
      cols = c(
        "source", "test_type", "df1", "df2", "test_value",
        "reported_p", "computed_p", "error", "decision_error"
      ),
      n = 20,
      char_width = 36
    ),
    digits = 4
  )
} else {
  cat("No statcheck output (package unavailable or no parseable report text).")
}
```

## Standardized Output Snapshot

```{r}
render_table(
  standardized,
  "No standardized rows available.",
  cols = c(
    "trial_id", "method", "metric", "value_numeric",
    "p_value", "anomaly_flag", "severity", "details"
  ),
  n = 20,
  digits = 4,
  char_width = 40
)
```

## Largest Rounding Deltas

```{r}
ranked <- row_results[order(-row_results$abs_percent_delta, na.last = TRUE), ]
knitr::kable(head(ranked[, c(
  "variable", "level", "group", "reported_percent", "computed_percent", "abs_percent_delta"
)], 15), digits = 4)
```

## Diagnostics

```{r}
hist(
  row_results$abs_percent_delta,
  breaks = 10,
  col = "gray80",
  border = "white",
  main = "Absolute Percent Delta Distribution",
  xlab = "|reported_percent - computed_percent|"
)
abline(v = 0.2, col = "red", lwd = 2, lty = 2)
```
