---
title: "Meta-Forensics Aggregation Audit"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report aggregates category-level forensic summaries into an evidence-burden triage aid for human review. It is not an automated assessment of study quality, validity, or misconduct.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("FORENSICS_STUDY_ID", "lungtime")
report_dir <- file.path(repo_root, "reports", "meta", study_id)

required <- c("meta_category_scores_out.csv", "meta_overall_summary.csv")
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

scores <- read.csv(file.path(report_dir, "meta_category_scores_out.csv"), check.names = FALSE)
overall <- read.csv(file.path(report_dir, "meta_overall_summary.csv"), check.names = FALSE)
```

## Interpretation Key

- `anomaly_score` (category): legacy column name for normalized evidence-burden contribution.
- `evidence_burden_score`: weighted combination of category evidence-burden indicators.
- `review_priority`: coarse triage label (`low`, `moderate`, `high`, `insufficient_data`) for human review priority.
- `overall_score` and `risk_tier`: backward-compatible aliases preserved for older consumers.

```{r}
knitr::kable(overall, digits = 4)
```

## Category Contribution Table

```{r}
knitr::kable(scores, digits = 4)
```

## Category Score Plot

```{r}
barplot(
  height = scores$anomaly_score,
  names.arg = scores$category,
  col = "gray75",
  border = NA,
  ylim = c(0, 1),
  main = "Category Evidence-Burden Contributions",
  ylab = "evidence burden"
)
abline(h = c(0.2, 0.45), col = "red", lty = 2)
```
