---
title: "Prediction-Validation Manuscript Review"
format:
  pdf:
    toc: true
    number-sections: true
execute:
  echo: true
  warning: false
  message: false
---

## Scope

This report screens a nonrandomized prediction-validation manuscript for internal statistical consistency.

It is intentionally narrower than the trial-oriented pipeline:

- `statcheck` is treated as a supplemental text screen only
- Table 2 is checked for summary-statistic reproducibility where the published rows allow it
- Table 3 is checked for integer confusion-matrix compatibility
- Table E2 is checked for calibration-decile arithmetic and approximate Hosmer-Lemeshow consistency
- Figure 1 is checked for cohort-flow arithmetic

All flagged results are screening signals, not adjudications.

## Load Outputs

```{r}
repo_root <- normalizePath("..", winslash = "/", mustWork = TRUE)
study_id <- Sys.getenv("REVIEW_STUDY_ID", unset = "")
if (!nzchar(study_id)) {
  stop("Missing REVIEW_STUDY_ID environment variable.")
}
report_dir <- file.path(repo_root, "reports", "reviews", study_id)
data_dir <- file.path(repo_root, "data", "processed", "reviews", study_id)

required <- c(
  "review_summary.csv",
  "review_table2_reproducibility.csv",
  "review_table3_metric_checks.csv",
  "review_calibration_checks.csv",
  "review_flow_checks.csv",
  "review_standardized_results.csv"
)
missing <- required[!file.exists(file.path(report_dir, required))]
if (length(missing) > 0) {
  stop("Missing files: ", paste(missing, collapse = ", "))
}

review_summary <- read.csv(file.path(report_dir, "review_summary.csv"), check.names = FALSE)
table2_checks <- read.csv(file.path(report_dir, "review_table2_reproducibility.csv"), check.names = FALSE)
table3_checks <- read.csv(file.path(report_dir, "review_table3_metric_checks.csv"), check.names = FALSE)
calibration_checks <- read.csv(file.path(report_dir, "review_calibration_checks.csv"), check.names = FALSE)
flow_checks <- read.csv(file.path(report_dir, "review_flow_checks.csv"), check.names = FALSE)
standardized <- read.csv(file.path(report_dir, "review_standardized_results.csv"), check.names = FALSE)

statcheck_raw <- if (file.exists(file.path(report_dir, "numeric_statcheck_raw.csv"))) {
  read.csv(file.path(report_dir, "numeric_statcheck_raw.csv"), check.names = FALSE)
} else {
  data.frame()
}
numeric_pkg_status <- if (file.exists(file.path(report_dir, "numeric_package_status.csv"))) {
  read.csv(file.path(report_dir, "numeric_package_status.csv"), check.names = FALSE)
} else {
  data.frame()
}
visual_summary <- if (file.exists(file.path(report_dir, "visual_summary.csv"))) {
  read.csv(file.path(report_dir, "visual_summary.csv"), check.names = FALSE)
} else {
  data.frame()
}
visual_rows <- if (file.exists(file.path(report_dir, "visual_row_results.csv"))) {
  read.csv(file.path(report_dir, "visual_row_results.csv"), check.names = FALSE)
} else {
  data.frame()
}
confusion_candidates <- if (file.exists(file.path(data_dir, "inputs", "table3_confusion_matrix_matches.csv"))) {
  read.csv(file.path(data_dir, "inputs", "table3_confusion_matrix_matches.csv"), check.names = FALSE)
} else {
  data.frame()
}

compact_character <- function(x, width = 52) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  too_long <- nchar(x) > width
  x[too_long] <- paste0(substr(x[too_long], 1, width - 3), "...")
  x
}

compact_df <- function(df, cols = NULL, n = 20, char_width = 52) {
  out <- df
  if (!is.null(cols)) {
    keep <- intersect(cols, names(out))
    out <- out[, keep, drop = FALSE]
  }
  if (nrow(out) > n) {
    out <- utils::head(out, n)
  }
  is_char_like <- vapply(out, function(col) is.character(col) || is.factor(col), logical(1))
  out[is_char_like] <- lapply(out[is_char_like], compact_character, width = char_width)
  out
}

render_table <- function(df, note, cols = NULL, n = 20, digits = 4, char_width = 52) {
  if (nrow(df) > 0) {
    knitr::kable(compact_df(df, cols = cols, n = n, char_width = char_width), digits = digits)
  } else {
    cat(note)
  }
}
```

## Summary

```{r}
knitr::kable(review_summary, digits = 4)
```

## Interpretation Key

- `statcheck_rows`, `statcheck_errors`, `statcheck_decision_errors`: APA-style inline test extraction yield and disagreement burden. Low counts are expected in prediction-model manuscripts.
- `grim_incons_cases`, `grimmer_incons_cases`, `duplicate_flag_rows`, `rounding_bias_flags`: numeric-integrity side screens carried over from the shared numeric pipeline.
- `table2_reproducible_rows`: Table 2 variables where the published summary statistics support a direct re-check.
- `table2_flagged_rows`: reproducible Table 2 rows with `|reported_p - recomputed_p| >= 0.05`.
- `exact_confusion_match_count`: number of integer confusion matrices that reproduce the rounded Table 3 sensitivity, specificity, PPV, and NPV simultaneously.
- `best_confusion_total_abs_delta`: smallest total mismatch across those four metrics when no exact match exists.
- `calibration_displayed_expected_events`: sum of displayed expected outcomes across Table E2 deciles.
- `flow_failed_checks`: number of arithmetic failures in the Figure 1 flow diagram.

## Text / Statcheck

```{r}
render_table(
  numeric_pkg_status,
  "No numeric package-status output.",
  cols = c("package", "installed", "version", "executed", "execution_note"),
  n = 20,
  char_width = 40
)
```

```{r}
render_table(
  statcheck_raw,
  "No statcheck rows were extracted from the manuscript text.",
  cols = c(
    "source", "test_type", "df1", "df2", "test_value",
    "reported_p", "computed_p", "error", "decision_error"
  ),
  n = 20,
  char_width = 36
)
```

## Table 2 Reproducibility

Rows listed as `not_reproducible_from_summary` are usually median/IQR rows where the manuscript does not publish enough information for an exact rerun.

```{r}
render_table(
  table2_checks,
  "No Table 2 reproducibility rows available.",
  cols = c(
    "variable",
    "measure_type",
    "reported_p",
    "recomputed_p",
    "abs_delta",
    "reproducible",
    "method_used",
    "anomaly_flag",
    "note"
  ),
  n = 25,
  char_width = 40
)
```

## Prediction Metrics

The main question here is whether the rounded Table 3 operating characteristics can come from any single integer confusion matrix with the reported sample size and event count.

```{r}
render_table(
  table3_checks,
  "No Table 3 metric checks available.",
  cols = c(
    "metric",
    "reported_value",
    "exact_match_count",
    "best_tp",
    "best_fp",
    "best_tn",
    "best_fn",
    "best_total_abs_delta",
    "anomaly_flag",
    "note"
  ),
  n = 10,
  char_width = 40
)
```

```{r}
render_table(
  confusion_candidates,
  "No confusion-matrix candidate table available.",
  cols = c(
    "tp",
    "fp",
    "tn",
    "fn",
    "sensitivity_calc",
    "specificity_calc",
    "ppv_calc",
    "npv_calc",
    "total_abs_delta",
    "exact_rounded_match"
  ),
  n = 10,
  char_width = 32
)
```

## Calibration

The Hosmer-Lemeshow calculation below is approximate because it uses the displayed rounded expected counts from Table E2 rather than the underlying model predictions.

```{r}
render_table(
  calibration_checks,
  "No calibration check rows available.",
  cols = c(
    "n_groups",
    "total_individuals_sum",
    "observed_outcomes_sum",
    "displayed_expected_outcomes_sum",
    "displayed_expected_minus_observed",
    "hl_statistic_from_displayed_rows",
    "hl_df",
    "hl_p_value_from_displayed_rows",
    "anomaly_flag",
    "note"
  ),
  n = 10,
  char_width = 40
)
```

## Flow Consistency

```{r}
render_table(
  flow_checks,
  "No flow-check rows available.",
  cols = c("check_name", "left_value", "right_value", "delta", "pass_flag", "note"),
  n = 10,
  char_width = 44
)
```

## Visual Checks

```{r}
render_table(
  visual_summary,
  "No visual summary output available.",
  n = 10,
  char_width = 36
)
```

```{r}
render_table(
  visual_rows,
  "No visual row-level output available.",
  n = 10,
  char_width = 36
)
```

## Standardized Review Output

```{r}
render_table(
  standardized,
  "No standardized review rows available.",
  cols = c(
    "trial_id",
    "method",
    "source_unit",
    "metric",
    "value_numeric",
    "p_value",
    "anomaly_flag",
    "severity",
    "details"
  ),
  n = 30,
  char_width = 40
)
```
